High resolution, annual maps of field boundaries for smallholder-dominated croplands at national scales

### 2021-10-16 inst/manuscript/manuscript.tex
Frontiers second revision, latex

The detail, temporal precision, and large extent of our maps was enabled
by our use of PlanetScope data, which is currently the only source of
sub-5 meter imagery with daily coverage (McCabe et al. 2017). These
spatial-temporal characteristics, together with the compositing
technique we developed, allowed us to develop a complete image catalog
for Ghana covering the two major seasons in the 2018 agricultural year.
Daily revisits were key to this capability, as they increased the number
of cloud-free observations that could be collected in each season. Over
rainy tropical regions, such as southern Ghana, the odds of obtaining a
single clear PlanetScope observation within a 1-2 week period is often
less than 50\% (Roy et al. 2021). Although Sentinel-2 is free and has
sufficient spatial resolution to effectively classify small-scale
croplands (e.g. Defourny et al. 2019, Kerner et al. 2020), its 5-day
interval is likely too infrequent to generate adequate seasonal
composites over much of Ghana. The smaller number of clear observations
that Sentinel-2 can provide compared to a daily acquisition schedule
would result in greater reflectance discontinuities and residual cloud
cover in the resulting composites. Given Ghana's persistent cloudiness,
such artifacts were present in a number of our PlanetScope composites.
However, these were not large enough to have an appreciable impact on
the resulting maps, as the mapping algorithms appeared to be relatively
insensitive to these anomalies and any discontinuities along tile
boundaries.

@@

\hypertarget{broader-applications}{%
\subsection{Broader applications}\label{broader-applications}}

This work demonstrates a proof of concept for developing high
resolution, annual maps of smallholder-dominated croplands at national
to regional scales, using an approach that follows recommended best
practices for training and assessing machine learning models (Elmes et
al. 2020). This approach can be readily updated to integrate
improvements, such as newer machine learning models. Beyond providing
valuable insights into field characteristics, field boundary maps can
help improve remote estimation of crop areas and yield (e.g. Estes et
al. 2013), and provide deeper insights into important socioeconomic
aspects of agricultural systems, such as the relationships between
agricultural productivity and farm size (Feder 1985, Carletto et al.
2013, Desiere and Jolliffe 2018). Such maps will be important for
understanding the rapid agricultural change that is currently occurring
in Africa.

\hypertarget{data-availability-and-usage}{%
\subsection{Data availability and
usage}\label{data-availability-and-usage}}

>>>>

The detail, temporal precision, and large extent of our maps was enabled
by our use of PlanetScope data, which is currently the only source of
sub-5 meter imagery with daily coverage (McCabe et al. 2017). These
spatial-temporal characteristics, together with the compositing
technique we developed, allowed us to create a complete image catalog
for Ghana covering the two major seasons in the 2018 agricultural year.
Daily revisits were key to this capability, as they increased the number
of cloud-free observations that could be collected in each season. Over
rainy tropical regions, such as southern Ghana, the odds of obtaining a
single clear PlanetScope observation within a 1-2 week period is often
less than 50\% (Roy et al. 2021). Although Sentinel-2 is free and has
sufficient spatial resolution to effectively classify small-scale
croplands (e.g. Defourny et al. 2019, Kerner et al. 2020), its 5-day
interval is likely too infrequent to generate adequate seasonal
composites over much of Ghana. The smaller number of clear observations
that Sentinel-2 can provide compared to a daily acquisition schedule
would result in greater reflectance discontinuities and residual cloud
cover in the resulting composites. Given Ghana's persistent cloudiness,
such artifacts were present in a number of our PlanetScope composites.
However, these were not large enough to have an appreciable impact on
the resulting maps, as the mapping algorithms appeared to be relatively
insensitive to these anomalies and any discontinuities along tile
boundaries.

@@

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

This work demonstrates a proof of concept for developing high
resolution, annual maps of field boundaries in smallholder-dominated
croplands at national to regional scales. The approach we used to
develop these maps includes a novel procedure for compositing daily
PlanetScope imagery, and follows recommended best practices for training
and assessing machine learning models (Elmes et al. 2020). Using
PlanetScope data enabled us to make a country-wide, high-resolution,
two-season catalog of imagery for a single year, even over areas with
frequent cloud cover. Methods to assess labeller accuracy and to create
consensus labels helped to minimize training label errors, which in turn
substantially improved the accuracy of the mapping model. Model
performance was further enhanced by using an active learning framework,
which selects the most informative training sample. This mapping
approach can be readily updated to integrate improvements, such as newer
machine learning models.

The resulting maps provide valuable information on Ghana's agricultural
systems, including an updated estimate of cropped area, and new data on
the characteristics of Ghana's cropping systems, such as the sizes and
numbers of fields. Beyond the information about field characteristics,
field boundary maps can help improve remote estimation of crop areas and
yield (e.g. Estes et al. 2013), and provide deeper insights into
important socioeconomic aspects of agricultural systems, such as the
relationships between agricultural productivity and farm size (Feder
1985, Carletto et al. 2013, Desiere and Jolliffe 2018). Such maps will
be important for understanding the rapid agricultural change that is
currently occurring in Africa.

\hypertarget{data-availability-and-usage}{%
\section{Data availability and
usage}\label{data-availability-and-usage}}
